% --------------------------------------------------------------
% This is all preamble stuff that you don't have to worry about.
% Head down to where it says "Start here"
% --------------------------------------------------------------

\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{tikz}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{proposition}[2][Proposition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------

%\renewcommand{\qedsymbol}{\filledbox}

\title{Homework 3}%replace X with the appropriate number
\author{Dustin Lambright - dalambri \\ Aseem Raina - araina \\ Bihan Zhang - bzhang28\\ %replace with your name
CSC 565 - Graph Theory} %if necessary, replace with your course title

\maketitle


\begin{question}{1}
Show that every simple graph $G$ with 6 vertices has either a clique of size 3 or an independent
set of size 3.
\end{question}

By the definition of inependent sets and cliques, any graph G with a clique of size n will also have a clique of n-1, n-2, ... n-(n-1).  The same goes for an independent set.  Therefore, using contradiction, if a graph does not have a clique of size 3 and does not have an independent set of size 3, the statement is false. \\ \\

The graph $K_{1,5}$ has a maximum clique size of 2, but an independent set of 5. (displayed in red)
\begin{align*}
\begin{tikzpicture}
\node[shape=circle,draw=black] (A) at (1,2) {A};
\node[shape=circle,draw=red] (B) at (2.4142857,2) {B};
\node[shape=circle,draw=red] (C) at (3.4142856,1) {C};
\node[shape=circle,draw=red] (D) at (2.4142857,0) {D};
\node[shape=circle,draw=red] (E) at (1,0) {E};
\node[shape=circle,draw=red] (F) at (0,1) {F};
\path [] (A) edge node[left] {} (B);
\path [] (A) edge node[left] {} (C);
\path [] (A) edge node[left] {} (D);
\path [] (A) edge node[left] {} (E);
\path [] (A) edge node[left] {} (F);
\end{tikzpicture}
\end{align*}

In an effort to reduce the size of the maximum independent set, edges are replaced, creating a cyclic graph: \\

\begin{align*}
\begin{tikzpicture}
\node[shape=circle,draw=red] (A) at (1,2) {A};
\node[shape=circle,draw=black] (B) at (2.4142857,2) {B};
\node[shape=circle,draw=red] (C) at (3.4142856,1) {C};
\node[shape=circle,draw=black] (D) at (2.4142857,0) {D};
\node[shape=circle,draw=red] (E) at (1,0) {E};
\node[shape=circle,draw=black] (F) at (0,1) {F};
\path [] (A) edge node[left] {} (B);
\path [] (B) edge node[left] {} (C);
\path [] (C) edge node[left] {} (D);
\path [] (D) edge node[left] {} (E);
\path [] (F) edge node[left] {} (A);
\path [] (E) edge node[left] {} (F);
\end{tikzpicture}
\end{align*}

This graph has a a maximum independent set of 3, and a maximum clique of 2. The only way to reduce the size of an independent set, i.e., $\{A,E,C\}$ is to connect any of those vertices with an edge.  The connection of any of these vertices results in a clique of size 3.  In an effort to maintain our clique constraint, if we remove the edges AF and AB to connect the independent set $\{A,E,C\}$, we end up with an independent set $\{A,F,B, D\}$.

\begin{align*}
\begin{tikzpicture}
\node[shape=circle,draw=red] (A) at (1,2) {A};
\node[shape=circle,draw=red] (B) at (2.4142857,2) {B};
\node[shape=circle,draw=black] (C) at (3.4142856,1) {C};
\node[shape=circle,draw=red] (D) at (2.4142857,0) {D};
\node[shape=circle,draw=black] (E) at (1,0) {E};
\node[shape=circle,draw=red] (F) at (0,1) {F};
\path [] (A) edge node[left] {} (C);
\path [] (B) edge node[left] {} (C);
\path [] (C) edge node[left] {} (D);
\path [] (D) edge node[left] {} (E);
\path [] (E) edge node[left] {} (A);
\path [] (E) edge node[left] {} (F);
\end{tikzpicture}
\end{align*}

The graph $C_6$ is the closest we can get to a graph without a clique of size 3 and without an independent set of size 3, but it has an independent set of size three, proving that a graph with a vertex count of 6 has to have an independent set of size 3 or a clique of size 3.

\begin{question}{2}
Prove or disprove: In a simple graph, every closed even trail of length more than 3 contains an
even cycle.
\end{question}

\begin{question}{3}
Prove the following by strong induction on the length of the trail: The edge set of every closed trail can be partitioned into one or more pairwise edge-disjoint cycles.
\end{question}

\textbf{i.} The edge set $E$ of every closed trail can be partitioned into one or more pairwise edge-disjoint cycles\\

Proof: Let $G$ be the graph containing the edge set $E$. \\

Let $n$ be the length of the maximum closed trial in $G$ of the form ($v_1$, $v_2$), ... ($v_n$, $v_1$). \\

Let $C$ be the smallest cycle in $G$ of the form ($v_i$, $v_{i+1}$)...($v_{i+k-1}$, $v_{i+k}$), where $v_i = v_{i+k}$ and $v_i$...$v_{i+k-1}$ are distinct (if the vertexes were not distinct that would mean it would be able to be partitioned into smaller cycles, and we started this exercise assuming C is the smallest cycle). \\

If $C = G$, the graph can be partitioned into one pairwise edge-disjoint cycle.\\

Otherwise, Let $G' = G - C$\\

The length of the closed trial through $G'$ cannot be more than $n$, and would have the closed trial ($v_1$, $v_2$)...($v_n$, $v_1$). \\

By induction we can partition the edge set of $G'$ into smaller disjoint cycles. Thus we show that the edge set of $G$ can be partitioned into disjoint cycles consisting of all the cycles in $G'$ and $C$\\

\textbf{ii.} If an edge set $E$ can be partitioned into one or more pairwise edge-disjoint cycles, it is a closed trial. \\

Proof: Let $G$ be the graph containing the edge set $E$.\\

If the edge set of $G$ can be partitioned into pairwise edge-disjoint cycles, every vertex must have an even degree (for v to be on a cycle it must have 2 degrees). Since every vertex is even $G$ must be Eulerian by Theorem 1.2.26. Every Eulerian graph must have a closed trial. Thus $G$ must have a closed trial.

\begin{question}{4}
Suppose that $T$ is a maximal trail in a simple graph $G$ and that $T$ has at least one edge and is not closed. Prove that the endpoints of T have odd degree.
\end{question}

Let $v_1$ and $v_n$ be the endpoints of $T$ (it must have at least 2 distinct vertexes, since it has at least one edge, and is not closed.). \\

Since $T$ is not closed, $v_1$ and $v_n$ cannot be connected. \\

If $v_1$ had a neighbors $v_0$, and their connected edge was not in $T$, it must be added in $T$ in order for $T$ to be maximal. Thus $v_1$ can only have one neighbor $v_2$. And any vertex, on a simple graph, with one neighbor has a degree of 1. The same argument can be applied to $v_n$ showing that it, also, has a degree of 1.

\begin{question}{5}
If G is a graph with vertices v1, v2, . . . , vn and Ak denotes the kth power of the adjacency matrix
of G under matrix multiplication then \\ \\
(***) $A^{k}[i, j]$ is the number of vi, vj -walks of length k in G. \\ \\
Show how to use (***) to solve the following without multipltying matrices and prove your answer
correct: Let A be the adjacency matrix of Kn. If i = j, then A3
[i, j] =\_\_\_\_ . Otherwise
A3
[i, j] = \_\_\_\_.
\end{question}

\begin{question}{6}
Draw a simple, connected graph with the following degree sequence, or prove that no such graph
is possible: \\
a. (3, 3, 3, 2, 2, 2) \\
b. (7, 6, 5, 4, 3, 2, 1) \\ 
c. (3, 3, 2, 2, 1, 1) \\
d. (7, 6, 5, 4, 3, 3, 2) \\
e. (6, 6, 5, 4, 3, 3, 1) 
\end{question}

\begin{question}{7}
 How many different simple graphs are there with 5 edges and with vertex set {v1, v2, . . . v5}?
(We are counting labeled graphs, not isomorphism classes)
\end{question}

\begin{question}{8}
Prove by contradiction: A graph with every vertex degree even has no cut-edge.
\end{question}




% --------------------------------------------------------------
%     You don't have to mess with anything below this line.
% --------------------------------------------------------------

\end{document}
